### 2023-02-07 article.tex
Progress

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Code must be extensively documented}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For code to be ideal paradata, it must be extensively documented.
This extend is determined by its intended use: 
to reproduce, replicate or extend \ref{sec:making-code-useful-paradata}.
The amount of documentation is, however, also determined
by the recommended practices for writing code in general.

@@

@@

As it is the code that is the most important actor in an the experiment,
it should be treated as equally or more important than the scientific
paper describing what is does.
Regardless of this, most academic journals, 
when concerning computational experiments
only review the (usually) English description of the code
and make the review of code optional.
One notable exception is rOpenSci \cite{ram2018community},
which is an organisation that does peer-review academic code 
and facilitates the optional publication of a paper.
Although both code and paper are peer-reviewed,
most effort is spent on reviewing the code,
as can be seen in, for example, 
the \verb|mcbette| R package \cite{bilderbeek2020mcbette}.
Within software development best-practices, 
code reviews are recommended as well \cite{wilson2014best}

% d: Documentation as a Factor for Project Popularity
%
% There exists a clear relationship between the popularity and the documentation effort [62], [64], [65]. 
% cosentino2017systematic

@@

@@

\paragraph{Need more training}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Code must be usefully documented}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For code to be ideal paradata, it must be usefully documented.
What is useful is determined by its intended use: 
to reproduce, replicate or extend \ref{sec:making-code-useful-paradata}.
The amount of documentation is, however, also determined
by the recommended practices for writing code in general.

@@

There exists a clear relationship between the popularity 
and the documentation effort \cite{cosentino2017systematic,hata2015characteristics}.

@@

More than half of all scientists have their code 
rarely or never reviewed \cite{vable2021code},
although code reviews are known to
accelerate learning of the developers,
improve the quality of the code
and resulting to an experiment that is likelier to be reproducible
\cite{vable2021code}.
One notable exception is rOpenSci \cite{ram2018community},
which is an organisation that does peer-review academic code 
and facilitates the optional publication of a paper.
Although both code and paper are peer-reviewed,
most effort is spent on reviewing the code,
as can be seen in, for example, 
the \verb|mcbette| R package \cite{bilderbeek2020mcbette}.
Within software development best-practices, 
code reviews are recommended as well \cite{wilson2014best}

@@

Coding errors are extremely common and contribute to the reproducibility crisis in science \cite{vable2021code}

%.
%. How to make more published research true
%. NIH plans to enhance reproducibility
%. The replication crisis in epidemiology: snowball, snow job, or winter solstice?
%. The harm done to reproducibility by the culture of null hypothesis significance testing

@@

\paragraph{Invest in training}

One needs to be trained to know the best practices,
before these can be applied. 
Articles that suggest these best practices, however, claim that this initial
investment pays off.
Code reviews are a good way to accelerate the 
learning of team members \cite{vable2021code}.
